LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-03-03 src/ms.tex
switch to SI units everywhere

\begin{equation}{}
\label{eq:energy_flx}
    \frac{dE}{dAdt} = \frac{1}{16\pi} \overline{\left[\left(\frac{dh_{+}}{dt}\right)^2 + \left(\frac{dh_{\times}}{dt}\right)^2\right]},
\end{equation}
where the bar indicates an average over several cycles of the wave which is appropriate for LISA sources. We can transform Eq.~\ref{eq:energy_flx} using Parseval's theorem, where we can write

\begin{align}
    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} &= \int_{0}^{\infty}df \int dA \frac{\pi f^2}{2} \left(|\tilde{h}_{+}|^2 + |\tilde{h}_{\times}|^2 \right).
\label{eq:Parseval}
\end{align}
Note that the factor of frequency squared comes from the Fourier transform of the square of the time derivative in Eq.~\ref{eq:Parseval}. Now, since $A = D_L^2 \Omega$ and $|\tilde{h}_{+,\times}|^2 = |\tilde{H}_{+,\times}|^2 / D_L^2$, we find
\begin{equation}{}
\label{eq:little_h_to_big}
    |\tilde{h}_{+,\times}|^2 dA = |\tilde{H}_{+,\times}|^2 d\Omega_{\iota,\beta},
\end{equation}
then we can write Eq.~\ref{eq:Parseval} in terms of $|H_{+,\times}|^2$ as 
\begin{equation}{}
    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} = \int_{0}^{\infty}df \frac{\pi f^2}{2} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right).
\label{eq:Parseval_2}
\end{equation}
Alternatively, by using Eq.~\ref{eq:little_h_to_big} and performing a Fourier transform we can also write that
\begin{equation}{}
    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} = \int_{0}^{\infty}df \int d\Omega \frac{dE}{d\Omega df}.
    \label{eq:deriv_relation}
\end{equation}
From inspection of Eq.~\ref{eq:Parseval_2} and Eq.~\ref{eq:deriv_relation}, we can write the spectral energy flux as
\begin{equation}{}
    \int d\Omega \frac{dE}{d\Omega df} = \frac{\pi f^2}{2} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right) .
    \label{eq:se_flux}
\end{equation}

\subsubsection{Fulled averaged SNR}
We are now in a position to write an expression for the fully averaged SNR. Note for brevity we write $\langle \rho \rangle^2$ when referring to $\langle \rho \rangle^2_{(\theta,\phi,\psi),(\iota,\beta)}$. The application of Eq.~\ref{eq:se_flux} to Eq.~\ref{eq:averaged_all} yields
\begin{equation}{}
    \langle \rho \rangle^2 = \frac{4}{D_L^2} \int_0^{\infty} df \frac{1}{P_{\rm n}(f)/\mathcal{R}(f)} \int \frac{d\Omega}{4\pi} \frac{dE}{d\Omega df} \frac{2}{\pi f^2}.
\end{equation}
This simplifies nicely to 
\begin{equation}{}
    \langle \rho \rangle^2 = \frac{2}{\pi^2 D_L^2}\int_0^{\infty}df \frac{dE}{df}\frac{1}{f^2 P_{\rm n}(f)/\mathcal{R}(f)}.
\end{equation}
Finally, noting that $dE/df = dE/dt \times dt/df = \dot{E}/\dot{f}$, we can use the definition of the characteristic strain from Eq.~\ref{eq:char_strain_dedf} (and use $c=G=1$),
\begin{equation}{}
    h_{c}^2 = \frac{1}{\pi^2 D_L^2} \left(\frac{2\dot{E}}{\dot{f}}\right),
\end{equation}
to finish up our position, direction, and orientation/polarisation averaged SNR as
\begin{equation}{}
    \langle \rho \rangle^2 = \int_0^{\infty}df \frac{h_{c}^2}{f^2P_{\rm n}(f)/\mathcal{R}(f)} = \int_0^{\infty}df \frac{h_{c}^2}{f^2 S_{\rm n}(f)},
    \label{eq:snr_finished_circ}
\end{equation}
where we have used that the effective power spectral density of the noise is defined as $S_{\rm n}(f) = P_{\rm n}(f) / \mathcal{R}(f)$.

>>>>

\begin{equation}{}
\label{eq:energy_flx}
    \frac{dE}{dAdt} = \frac{1}{16\pi} \referee{\frac{c^3}{G}} \overline{\left[\left(\frac{dh_{+}}{dt}\right)^2 + \left(\frac{dh_{\times}}{dt}\right)^2\right]},
\end{equation}
where the bar indicates an average over several cycles of the wave which is appropriate for LISA sources. We can transform Eq.~\ref{eq:energy_flx} using Parseval's theorem, where we can write

\begin{align}
    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} &= \int_{0}^{\infty}df \int dA \referee{\frac{c^3}{G}} \frac{\pi f^2}{2} \left(|\tilde{h}_{+}|^2 + |\tilde{h}_{\times}|^2 \right).
\label{eq:Parseval}
\end{align}
Note that the factor of frequency squared comes from the Fourier transform of the square of the time derivative in Eq.~\ref{eq:Parseval}. Now, since $A = D_L^2 \Omega$ and $|\tilde{h}_{+,\times}|^2 = |\tilde{H}_{+,\times}|^2 / D_L^2$, we find
\begin{equation}{}
\label{eq:little_h_to_big}
    |\tilde{h}_{+,\times}|^2 dA = |\tilde{H}_{+,\times}|^2 d\Omega_{\iota,\beta},
\end{equation}
then we can write Eq.~\ref{eq:Parseval} in terms of $|H_{+,\times}|^2$ as 
\begin{equation}{}
    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} = \int_{0}^{\infty}df \frac{\pi f^2 \referee{c^3}}{2 \referee{G}} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right).
\label{eq:Parseval_2}
\end{equation}
Alternatively, by using Eq.~\ref{eq:little_h_to_big} and performing a Fourier transform we can also write that
\begin{equation}{}
    \int_{-\infty}^{+\infty}dt\int dA \frac{dE}{dAdt} = \int_{0}^{\infty}df \int d\Omega \frac{dE}{d\Omega df}.
    \label{eq:deriv_relation}
\end{equation}
From inspection of Eq.~\ref{eq:Parseval_2} and Eq.~\ref{eq:deriv_relation}, we can write the spectral energy flux as
\begin{equation}{}
    \int d\Omega \frac{dE}{d\Omega df} = \frac{\pi f^2 \referee{c^3}}{2 \referee{G}} \int d\Omega \left(|\tilde{H}_{+}|^2 + |\tilde{H}_{\times}|^2 \right) .
    \label{eq:se_flux}
\end{equation}

\subsubsection{Fulled averaged SNR}
We are now in a position to write an expression for the fully averaged SNR. Note for brevity we write $\langle \rho \rangle^2$ when referring to $\langle \rho \rangle^2_{(\theta,\phi,\psi),(\iota,\beta)}$. The application of Eq.~\ref{eq:se_flux} to Eq.~\ref{eq:averaged_all} yields
\begin{equation}{}
    \langle \rho \rangle^2 = \frac{4 \referee{G}}{\referee{c^3} D_L^2}\int_0^{\infty} df \frac{1}{P_{\rm n}(f)/\mathcal{R}(f)} \int \frac{d\Omega}{4\pi} \frac{dE}{d\Omega df} \frac{2}{\pi f^2}.
\end{equation}
This simplifies nicely to 
\begin{equation}{}
    \langle \rho \rangle^2 = \frac{2 \referee{G}}{\pi^2 \referee{c^3} D_L^2} \int_0^{\infty}df \frac{dE}{df}\frac{1}{f^2 P_{\rm n}(f)/\mathcal{R}(f)}.
\end{equation}
Finally, noting that $dE/df = dE/dt \times dt/df = \dot{E}/\dot{f}$, we can use the definition of the characteristic strain from Eq.~\ref{eq:char_strain_dedf} to finish up our position, direction, and orientation/polarisation averaged SNR as
\begin{equation}{}
    \langle \rho \rangle^2 = \int_0^{\infty}df \frac{h_{c}^2}{f^2P_{\rm n}(f)/\mathcal{R}(f)} = \int_0^{\infty}df \frac{h_{c}^2}{f^2 S_{\rm n}(f)},
    \label{eq:snr_finished_circ}
\end{equation}
where we have used that the effective power spectral density of the noise is defined as $S_{\rm n}(f) = P_{\rm n}(f) / \mathcal{R}(f)$.
